Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-09-02 doc/paper.tex
udapte

      One additional criterion can be given as a measure of intersection between one set  $S_{p_i}$ and 
      and the other sets $S_{p_j}$, $j \neq i$ as follow:
      \begin{align}\label{eq:intersection-heuristic}
      	   g(s^P,p_i) = \frac{\sum_{p_j \in V \setminus s^P: p_i \neq p_j}|S_{p_i} \cap S_{p_j}|}{|V|-|s^P|-1}, p_i \in V \setminus s^P,
      \end{align}
      where $|S_{p_i} \cap S_{p_j}|$ denotes the surface (in some unit) of the intersection of the two 
      visible regions. If some set $S_{p_i}$ has less intersection with the  visible regions of other candidate guards it is more likely that $p_i$ will be a good candidate for a guard. So, based on it, we try to always add a vertex $p_j$ to $s^P$ which has the smallest $g$ value acc. to formula~(\ref{eq:intersection-heuristic})

@@

>>>>

      One additional criterion can be given as a measure of intersection between one set  $S_{p_i}$ and 
      and the other sets $S_{p_j}$, $j \neq i$ as follow:
      \begin{align}\label{eq:intersection-heuristic}
      	   g(s^P,p_i) = \frac{\sum_{p_j \in V \setminus s^P: p_i \neq p_j}|S_{p_i} \cap S_{p_j}|}{|V|-|s^P|-1}, p_i \in V \setminus s^P,
      \end{align}
      where $|S_{p_i} \cap S_{p_j}|$ denotes the measure of surface (in some unit) of the intersection for the two 
      visible regions. If some set $S_{p_i}$ has less intersection with the  visible regions of other candidate guards it is more likely that $p_i$ will be a good candidate for a guard. So, based on it, we try to always add a vertex $p_j$ to $s^P$ which has the smallest $g$ value acc. to formula~(\ref{eq:intersection-heuristic})

@@

     \subsection{Beam Search (BS)}
        BS is an incomplete BFS heuristic search algorithm.
